CLT Results

### 2022-04-02 analysis/clt_irt_analysis.Rmd
fix aoa

aoa <-  read_xlsx("../data/word_list.xlsx")%>%
  select(german,english, aoa_german_comb)%>%
  filter(german != "rakete")%>%
  rename(targetWord = english)%>%
  mutate(targetWord = ifelse(targetWord == "frying pan", "fryingpan", targetWord),
         targetWord = ifelse(targetWord == "courgette", "zucchini", targetWord),
         targetWord = ifelse(targetWord == "rocket", "arugula", targetWord),
         targetWord = ifelse(targetWord == "palm tree", "palmtree", targetWord))%>%
  filter(german != "kappe", 
         german != "karotte", 
         german != "mohrrübe")%>%
  distinct(german, .keep_all = T)%>%
  mutate(group = cut(aoa_german_comb, 
                   breaks=c(0, 3.5, 6, Inf), 
                   labels=c("low","middle","high")))
```

>>>>

aoa <-  read_xlsx("../data/word_list.xlsx")%>%
  select(german,english, aoa_german_comb)%>%
  filter(german != "rakete",
         german != "hobel")%>%
  rename(targetWord = english)%>%
  mutate(targetWord = ifelse(targetWord == "frying pan", "fryingpan", targetWord),
         targetWord = ifelse(targetWord == "courgette", "zucchini", targetWord),
         targetWord = ifelse(targetWord == "rocket", "arugula", targetWord),
         targetWord = ifelse(targetWord == "palm tree", "palmtree", targetWord),
         targetWord = ifelse(targetWord == "airplane", "plane", targetWord))%>%
  filter(german != "kappe", 
         german != "karotte", 
         german != "mohrrübe")%>%
  distinct(german, .keep_all = T)%>%
  mutate(group = cut(aoa_german_comb, 
                   breaks=c(0, 3.5, 6, Inf), 
                   labels=c("low","middle","high")))
```
